What's in a Domain? Anaylsis of URL Features

### 2022-09-19 paper/paper.tex
Literature

The Uniform Resource Locator (URL) is now a ubiquitous element of modern life. 
We use them to advertise and locate businesses, to retrieve news and media and 
to interact with other people across a broad of social applications. It should
be no surprise that processing URLs is key component of many tasks that involve
analysing internet data. In many applications the URL is the central piece of 
information available because the demands of the task require immediate analysis.
Prominent examples include security analysis of potenital phishing attacks\cite{Basnet2014}, 
detection of potential spam emails \cite{}, and applications to online advertsing
including anticipation of conversions \cite{Qiu2020} or contextual analysis of
the content of webpages\cite{Kan2005,Baykan2009}.

@@

Multiple data science and machine learning applications on internet data 
Write a literature review \cite{Vazhayil2018}
\cite{Canali2011}
\cite{Ayes2019}
\cite{Mamun2016}
\cite{Li2020}
\cite{Basnet2012}
\cite{Basnet2014}
\cite{Tupsamudre2019}
\cite{Le2018}
\cite{Baykan2009}
\cite{Kan2005}
\cite{Hernandez2012}
\cite{Chung2010}
\cite{Qiu2020}
\cite{Vaishnavi2021}
\cite{Xu2021}
\cite{Rhea2022}

>>>>

The Uniform Resource Locator (URL) is now a ubiquitous element of modern life. 
We use them to advertise and locate businesses, to retrieve news and media and 
to interact with other people across a broad of social applications. It should
be no surprise that processing URLs is key component of many tasks that involve
analysing internet data. In many applications the URL is the central piece of 
information available because the demands of the task require immediate analysis.
Prominent examples include security analysis of potenital phishing attacks\cite{Basnet2014}, 
detection of potential spam emails \cite{}, and applications to online advertsing
including anticipation of conversions \cite{Qiu2020} or contextual analysis of
the content\cite{Kan2005,Baykan2009} or language\cite{Baykan2013} of webpages.

@@

Multiple data science and machine learning applications on internet data 
Write a literature review \cite{Vazhayil2018}
\cite{Canali2011}
\cite{Ayes2019}
\cite{Mamun2016}
\cite{Li2020}
\cite{Basnet2012}
\cite{Basnet2014}
\cite{Tupsamudre2019}
\cite{Le2018}
\cite{Baykan2009}
\cite{Kan2005}
\cite{Hernandez2012}
\cite{Chung2010}
\cite{Qiu2020}
\cite{Vaishnavi2021}
\cite{Xu2021}
\cite{Rhea2022}
\cite{Ma2009}
\cite{Verma2017}
\cite{Sountharrajan2020}
